Redundant calibration as a complex optimization problem

### 2017-12-15 paper.tex
Gianni's last comments

%\title[Complex redundant calibration]{Redundant calibration as a complex optimization problem}
\title[Redundant interferometric calibration as a complex optimization problem]{Redundant calibration as a complex optimization problem}
%\author[T.L.~Grobler et al.]{T.L.~Grobler$^{1}$\thanks{E-mail: email@address (AVR)}, G.~Bernardi$^{1,2}$, Z.S.~Ali$^{3}$?, C.L.~Carilli$^{4,5}$?, J.S.~Dillon$^{3}$?, A.~Liu$^{3}$?, \newauthor
%A.R.~Parsons$^{3,6}$? and O.M.~Smirnov$^{1,2}$?\\
%$^{1}$Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa\\
%$^{2}$SKA SA, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa\\
%$^{3}$Dept. of Astronomy, University of California, Berkeley, CA 94720, USA\\
%$^{4}$National Radio Astronomy Obs., Socorro NM\\
%$^{5}$Cavendish Lab., Cambridge UK\\
%$^{6}$Radio Astronomy Lab., U. California, Berkeley CA 94720, USA}
\author[T.L.~Grobler et al.]{T.L.~Grobler$^{1,2}$\thanks{E-mail: email@address (AVR)}, G.~Bernardi$^{2,3}$, C.L.~Carilli$^{4,5}$, J.S.~Kenyon$^{2}$, A.R.~Parsons$^{6,7}$? \newauthor and O.M.~Smirnov$^{2,3}$\\
$^{1}$Dept of Mathematical Sciences, Computer Science Division, Stellenbosch University, Private Bag X1, 7602 Matieland, South Africa\\
$^{2}$Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa\\
$^{3}$SKA SA, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa\\
$^{4}$National Radio Astronomy Obs., Socorro NM\\
$^{5}$Cavendish Lab., Cambridge UK\\
$^{6}$Dept. of Astronomy, University of California, Berkeley, CA 94720, USA\\
$^{7}$Radio Astronomy Lab., U. California, Berkeley CA 94720, USA}
\begin{document}

>>>>

%\title[Complex redundant calibration]{Redundant calibration as a complex optimization problem}
\title[Redundant interferometric calibration as a complex optimization problem]{Redundant calibration as a complex optimization problem}
%\author[T.L.~Grobler et al.]{T.L.~Grobler$^{1}$\thanks{E-mail: email@address (AVR)}, G.~Bernardi$^{1,2}$, Z.S.~Ali$^{3}$?, C.L.~Carilli$^{4,5}$?, J.S.~Dillon$^{3}$?, A.~Liu$^{3}$?, \newauthor
%A.R.~Parsons$^{3,6}$? and O.M.~Smirnov$^{1,2}$?\\
%$^{1}$Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa\\
%$^{2}$SKA SA, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa\\
%$^{3}$Dept. of Astronomy, University of California, Berkeley, CA 94720, USA\\
%$^{4}$National Radio Astronomy Obs., Socorro NM\\
%$^{5}$Cavendish Lab., Cambridge UK\\
%$^{6}$Radio Astronomy Lab., U. California, Berkeley CA 94720, USA}
\author[T.L.~Grobler et al.]{T.L.~Grobler$^{1,2}$\thanks{E-mail:tlgrobler@sun.ac.za}, G.~Bernardi$^{2,3,4}$, J.S.~Kenyon$^{2}$, A.R.~Parsons$^{5,6}$ and O.M.~Smirnov$^{2,3}$\\
$^{1}$Dept of Mathematical Sciences, Computer Science Division, Stellenbosch University, Private Bag X1, 7602 Matieland, South Africa\\
$^{2}$Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa\\
$^{3}$SKA SA, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa\\
$^{4}$INAF-Istituto di Radioastronomia, via Gobetti 101, 40129, Bologna, Italy\\
$^{5}$Dept. of Astronomy, University of California, Berkeley, CA 94720, USA\\
$^{6}$Radio Astronomy Lab., U. California, Berkeley CA 94720, USA}
\begin{document}
